Edge sign prediction in general graphs and connection with Correlation Clustering

### 2017-06-28 lowstretch_and_cc.tex
start describing galaxy tree algorithm
add support files for tikz drawing
add a notations table
typos
add a short intro to explain why we build our tree

\title{Edge sign prediction in general graphs and connection with Correlation Clustering}

\begin{document}
\newgeometry{vmargin=1.5cm,left=1.5cm,textwidth=130mm,marginparsep=5mm,marginparwidth=52mm}
\maketitle
% \tableofcontents

@@

@@

@@

@@

@@

\input{gtx_experiments}

>>>>

\title{Edge sign prediction in general graphs and connection with Correlation Clustering}
% \usetikzlibrary{external}
% \tikzexternalize[mode=list and make, failed ref warnings for={\ref,\cite,\pageref},]
\begin{document}
\newgeometry{vmargin=1.3cm,left=1.5cm,textwidth=130mm,marginparsep=5mm,marginparwidth=52mm}
\maketitle
% \tableofcontents

% \input{notations}

@@

% ICML paper this year that touch something very related multicut and give recent applications in
% vision https://arxiv.org/abs/1503.03791

@@

\newpage

@@

\input{notations}

Given a graph $G$, and following the social balance theory roughly summarized as \enquote{the enemy
of my enemy is my friend}, assume that the labelling of $E$ is consistent with a two-clustering of
$V$. Namely, assume that $V$ can be partitioned in two clusters such that edges within each cluster
are positive and edges across clusters are negative. In that case, the following
\emph{multiplicative rule} holds: for any nodes $u$, $v$ in $V$, and any path $p$ between $u$ and
$v$ in $G$, the sign $\yuv$ is equal to the product of the signs along $p$ (we call this product the
parity of $p$ and denote it $\pi(p)$). While it is a simple and convenient model, this is too strong
of a requirement to be satisfied in practice. Therefore, we relax it by assuming that we start with
a consistent labeling $Y$ but can only observe a randomly perturbed version $Y'$ of $Y$.
Specifically, given a constant $q\in [0, \nicefrac{1}{2})$, each sign of $Y$ is flipped with a
probability smaller than $q$.

In this section, we are interested in active learning algorithms, that first query a subset
$\etrain$ of the edges, observe the signs in $\etest$ and use them to predict the remaining signs.
More precisely, we focus on an algorithm that query a spanning tree $T$ of $G$ and predict the sign
of an edge $(u,v) \in \etest = E \setminus E_T$ as the parity of $\pathtuv$. While this
can\Todo{state it formally then ;)} be stated more formally~\autocite[Section
4.1]{Cesa-Bianchi2012b}, it makes sense intuitively that since each sign has been potentially
flipped, the longer the path in $T$, the more likely its parity will be not be equal to the truth
$\yuv{}$. Therefore we would like each such path to be as short as possible and in the rest of this
section, we describe a way to build spanning tree tailored for this situation.

@@

\input{gtx_algorithm}

@@

% \input{gtx_experiments}
